% ABSTRACT IN ENGLISH
Metal Additive Manufacturing (AM) techniques, often called 3D printing, introduce innovative production processes for crafting metal components through incremental material deposition, layer after layer. These technologies allow the production of complex shapes, lightweight structures, internal features, and surface patterns that can not be achieved with traditional methods. Recent technology development has accelerated the industrial adoption of metal AM procedures, particularly Electron Beam Melting and Selective Laser Sintering processes involving selective melting of metal powders using an external source of contained energy.
This thesis undertakes a comprehensive appraisal of powder bed fusion technologies, providing an in-depth evaluation of operational principles, challenges, benefits, and critical issues compared with other processes, the typical defects, and approaches to defect them. The main topic of this thesis is "hot spot" defect detection, which are localized zones exhibiting elevated temperatures for a sustained time and slower cooling drift, often attributable to their proximity to adjacent loose powder. In metal AM, temperature assumes a particular significance as most defects are due to anomalous thermal conditions. Moreover, a component's thermal history significantly influences the finished product's critical aspects, including porosity, microstructure, and geometry. Thus, it is essential to correctly understand and analyze the thermal history of the printed part, especially during the test and certification phase. The thesis also presents an algorithm for clustering areas on the build plate that share analogous thermal histories through functional data analysis. The thesis also proposes an implementation of the algorithm in Python.
\\[0.5cm]
\textbf{Keywords:} metal additive manufacturing, powder bed fusion, defect detection, hot-spot, machine learning, functional data analysis

% 1782 caratteri
