Additive manufacturing (AM) is described in ISO/ASTM 52900 \cite{international_standard_organization_isoastm_2015} as the "process of joining materials to make parts from 3D model data, usually layer upon layer, as opposed to subtractive manufacturing and formative manufacturing methodologies".
In this first chapter, we will discuss and describe new AM processes or, popularly, 3D printing, which will most likely characterize the manufacturing scenario in upcoming years. Although the adjective "new" may not be quite appropriate, after all. Before being called AM processes, in fact, these processes were called "Rapid prototyping" (RP). From the name, it is easy to understand why this technology was developed: already from the 1950s - 1960s, there was the idea about a lean approach to new product development process, a new approach that would allow to contain costs and reduce. It was only in 1984 and 1986 that the first 3D printing technologies were patented and the possibility of manufacturing a finished object by adding material layer by layer became a reality. The early 2000s were characterized by a push towards the use of these technologies also for large-scale production, trying to unlink RP from the research and development process alone. In fact, it was in these years that the first cost studies associated with 3D printing usage for mass production were conducted, among which it's worth mentioning \citeauthor{hopkinson_analysis_2003} (\citeyear{hopkinson_analysis_2003}). The real breakthrough for popular 3D printing occurred in the early 2010s, when patents for some polymers used in fused deposition modeling systems (FDM) expired, and there was a real explosion of producers of these polymers and FDM 3D printers. We will discuss about FDM shortly. Nowadays, additive manufacturing is mainly used for the production of small batches of finished products, sometimes even single-unit batches, in the prototyping phase of a new product and in processes which require a very high degree of customization. Moreover, AM processes allow for the creation of complex geometries, objects and patterns that are not achievable with traditional manufacturing processes. As we will see in \textit{Chapter ~\ref{ch:Metal_AM_and_lattice}}, a typical example are lattice structures. 
I want to emphasize from the very beginning that these manufacturing processes do not intend to replace the traditional ones, but rather allow us to expand the limits of what the human being is capable of manufacturing. It's important to understand that additive manufacturing will enable us to obtain components with mechanical functionalities and complexity that were once unimaginable with traditional manufacturing processes, and it could also represent a breakthrough in environmental sustainability by reducing waste of materials. This will become even clearer in section \ref{sec:economic_strategic_social}, when we will consider cost factors.


\section{Additive Manufacturing Process Categories} \label{sec:AMproc}
According to ISO/ASTM 52900 \cite{international_standard_organization_isoastm_2015} and \citeauthor{gibson_additive_2015} there are seven different types of AM technologies: vat photopolymerization processes, extrusion-based systems, material jetting, binder jetting, sheet lamination processes, powder bed fusion processes and direct energy deposition processes. Now we will briefly discuss about the differents technologies and in \textit{Chapter~ \ref{ch:Metal_AM_and_lattice}} we will focus on AM of metals and powder bed fusion 3d printers.
\begin{itemize}
    \item \textbf{Vat photo-polymerization processes} (VP): VP processes use radiation-curable resins or photopolymers that can be solidified using controlled light sources, usually ultraviolet radiation, but also visible light. Typically, lasers are directed using scanning galvanometers, Digital Micromirror Devices\textsuperscript{TM}, or multiple directional light sources such as the two-photon system or controlled LEDs. The polymers used in this printing technology are usually acrylate~-~based resins or epoxy resins, but also industrial ceramic materials, such as alumina, zirconia and silicone nitride. In recent years, new materials have been developed for the production of investment casting patterns \cite{3d_systems_investment_nodate}, but also high technical performances material such as including cyanate ester, which is used with Carbon Digital Light Synthesis\textsuperscript{TM} to produce finished pieces capable of withstanding high pressures (up to 3800-4000 MPa)\cite{carbon_what_nodate}. The major advantages of this technology are the high level of accuracy of the finished products (up to 0.05 millimeters), relatively high speed of manufacturing, and the variety of print sizes (ranging from very small printers to larger ones, up to 1000 mm x 800 mm x 500 mm). The disadvantages are that the finished prints require significant post-processing, the printers and the process are still quite expensive, material choices are limited to photo-polymers only, and the need to print support structures that are important to prevent the final piece from collapsing.
    \item \textbf{Extrusion-based systems} of \textbf{fused filament fabrication} (FFF): FFF systems selectively extrude material, usually in the form of a filament, through a heated nozzle or orifice. The FDM 3D printers we discussed earlier fall into this category and are characterized by a nozzle that is free to move in the horizontal plane and a platform that moves up and down along the z-axis to allow for laerwise material deposition. Typically, materials used with this type of AM are waxes, polyamide, acrylonitrile-butadiene-styrene, polyphenyl sulfone, polycarbonate, ceramics as well as biocompatible or biodegradable materials. The main advantages of FFF systems include their widespread popularity and economic accessibility, as well as the variety of materials that can be used, such as ABS, which provides excellent structural properties, or PLA (polylactic acid), which can be extruded at relatively low temperatures and it is compostable. The drawbacks of this technology include lower print speeds and a lower achievable minimum resolution if compared to other processes, as well as a greater need for post-processing to achieve the desired finishing.
    \item \textbf{Material jetting systems} (MJ): MJ is a technique that allows 3D printing of a piece using tiny droplets of liquid material that are selectively deposited onto a surface. As always, the object is developed adding new material according to a layer-wise logic. In a certain way, material jetting can be seen as the natural evolution of normal 2D inkjet printers but in three dimensions. Just like inkjet printers, in MJ there can be different "cartridges" of materials and colors. In fact, one of the main advantages of MJ is the possibility of printing high-resolution multi-colored or multi-material objects. Initially, the materials used with this technology were waxes, but in recent years the focus has been more on the deposition of acrylate photopolymers, which droplets of materials are solidified with an UV lamp directly attached to print nozzle. The main advantages of MJ are the almost absence of material waste, as the deposition-on-demand process is extremely precise (droplets of \SIrange{25}{120}{\micro\meter} at a rate of 0-2000 drops per second), and the possibility, as mentioned earlier, of using different materials and colors simultaneously. The disadvantages of this solution are mostly the limited number of usable materials, since only polymers and waxes can be used and only materials that are not excessively viscous. Furthermore, the process and equipment required are relatively inexpensive and capable of printing at a sustained speed.
    \item \textbf{Binder jetting systems}: Binder jetting, is very similar to MJ. In binder jetting, a liquid binding agent called "binder" is selectively deposited in small droplets to solidify powdered materials and allow different layers of powder to stick together. Due to the production method, the final objects may not always be suitable for withstanding large structural stresses and often require a long post-processing phase, which could increase variable costs. Binder jetting can be used with both thermo-plastic polymers and metals, as well as ceramic materials. The major advantages of this technology compared to MJ are the ability to use a much wider range of materials and the higher speed of printing. Additionally, it is possible to mix different powders to obtain final objects with different mechanical properties. The disadvantages, as mentioned earlier, are the fact that printed parts may not always be suitable to be used as structural parts and the costly post-processing operations necessary to improve the mechanical characteristics of the finished pieces.
    \item \textbf{Sheet lamination} (LOM): In sheet lamination or laminated object manufacturing (LOM), a 3D printing technique, layers of material are bonded together to form a final object. So, each layer of the final object is made up of a sheet of laminate. There are two different approaches: "bond-then-form" and "form-then-bond". In the first case, the laminate is positioned and bonded to the substrate, and then cut following the model contour. In the second case, the laminate material is first cut and then placed on the substrate and bonded to the underlying layer. LOM techniques allow the usage of wood, thermo-plastic polymers, industrial ceramics, as well as paper, polyvinyl chloride, and composite materials. The major advantages of LOM are the ability to print very large parts quickly and the much lower fixed equipment costs compared to other types of AM processes.
    \item \textbf{Powder bed fusion} (PBF): PBF is also called direc metal laser sintering (DMLS) or selective laser melting (SLM). In these additive manufacturing techniques, a concentrated energy source is used to selectively melt layers of powder. Usually, the energy source is a laser or an electron beam and the materials used can be polyamides, nylons, elastomers, as well as metals such as stainless steel, titanium, aluminum, cobalt, and copper. It's important to note that this AM technique is widely used for direct manufacturing and allows for the production of finished objects with excellent mechanical properties and surface finishes, mostly used in automotive, aerospace, or biomedical industries.
    \item \textbf{Direct energy deposition systems} (DED): in DED, a concentrated heat energy source is used to selectively melt deposited material as soon as it is deposited. Depending on the energy source used, we can further divide the processes into laser metal deposition, electron beam metal deposition, and plasma metal deposition. Moreover, depending on the shape of the material used, we can distinguish between powder-fed and wire-fed systems. Finally, depending on the direction in which the material is fed, we can distinguish between off-axis feeding, in which the material is deposited by a side-mounted incident nozzle, and coaxial feeding systems, in which the powder or wire material is deposited co-axially with the energy beam. The major advantages of DED are that it can be used to add parts to existing components or repair broken components with ease, the ability to print parts with very steep angles without requiring support, the wide range of powders available, the large printing area that can be achieved, and the ability to use various feeders. The disadvantages are that machining and post-processing are often required, overly complex shapes cannot be printed unlike with PBF systems, and overall process accuracy is lower compared to PBF.
    
\end{itemize}

\section{An Economic, Strategic and Social Perspective} \label{sec:economic_strategic_social}
In this section, we will discuss the advantages of additive manufacturing in terms of business strategy and the additive manufacturing market. Firstly, we will discuss the costs associated with additive manufacturing compared to traditional manufacturing processes. Next, we will analyze a framework for AM processes costing, and finally, we will examine the AM market and its evolution over time, with a small focus on the aspect of environmental sustainability. 



In addition to the value structure of the final product, additive manufacturing processes have completely changed the structure of production costs. We will talk about two different costing framework, the first proposed by \cite{ruffo_cost_2006} and the second proposed by \cite{hopkinson_analysis_2003}. The latter can be considered as a simplified version of the former. The cost of a finished product, manufactured either in traditional manufacturing processes or in AM processes is mainly formed by four factors:
\begin{itemize}
    \item \textbf{Material costs}: are costs associated to raw materials used during the manufacturing processes. As can be seen in \cite{thomas_costs_2014}, raw materials for AM processes have an higher price if compared to other "traditional" raw material (even if Acrylonitrile Butadiene Styrene and Polylactic Acid filaments are becoming cost competitive). However, in some AM processes, such as LPBF, the material waste is much lower if compared to traditional manufacturing processes, as it does not require support structures and excess powder can be easily recovered and reused. Therefore, when calculating costs, it is also important to consider potential material waste, both in economic and environmental terms. This relation is even more clear if we consider equation \ref{eq:material} 
    \begin{equation}\label{eq:material}
        C_1 = \frac{mC_m}{1-f}
    \end{equation}
    where $C_1$ are costs associated to raw materials, $m$ is the mass of the part, $C_m$ is the cost per unit mass and $f$ is the scrap rate, which can be seen as the portion of material wasted.
    \item \textbf{Cost of tooling}: this cost record refers to tooling dies, molds, and fixtures, and is the major cost advantage of AM processes compared to traditional manufacturing processes. In fact, with AM processes, there is no need to incur in fixed costs related to molds (so these costs do not need to be amortized), making AM particularly suitable for small to medium production batch. The cost can be computed as
    \begin{equation}
        C_2=\frac{C_t}{n}\ceil*{\frac{n}{n_t}}
    \end{equation}
    where $C_t$ is the cost of one set of tooling, $n$ is the number of units in production run in fixed time and $n_t$ is the number of units which each tool set can make before wearing out tool life.
    \item \textbf{Cost of equipment}: are all the costs related to the equipment needed in the manufacturing process to reach the desired production rate. In AM processes it might be just one working ideally at full capacity. It might be noticed that 3d printers costs are, as always in technology revolutions, decreasing over time, but are still quite high if compared to traditional machines such as CNC. The cost pert piece can be computed as
    \begin{equation}\label{eq:cost_equipment}
        C_3 = \frac{1}{\dot{n}} \cdot \left( \frac{C_c}{Lt_{WO}}\right)
    \end{equation}
    where $C_c$ is the cost equipment, $\dot{n}$ is the production rate, $L$ is the load factor which is the fraction of time for which the equipment is productive (thus the saturation rate of the equipment) and $t_{wo}$ is the lifetime of equipment computed as a simple straight line depreciation model.
    \item \textbf{Overhead cost}: are all indirect costs which can be imputed to the production of finished goods. Typical example of overhead costs are labor, facilities, energy and so on and so forth. In AM processes, OVH cost is dominated by pre and post-processing operations and energy cost. So, as we will see in \textit{Chapter ~ \ref{ch:Metal_AM_and_lattice}}, process monitoring and control is a key issue in AM processes. ndeed, by ensuring that the process is under control and the printers are properly calibrated, post-processing costs can be significantly reduced. Overhead costs can be computed as
    \begin{equation}\label{eq:OVH_cost}
        C_4 = \frac{\dot{C}_{OVH}}{\dot{n}}
    \end{equation}
    where $\dot{C}_{OVH}$ is overhead cost per hour and $\dot{n}$ is the production rate.
    \end{itemize}

In conclusion, additive manufacturing processes should not be seen as substitutes for traditional manufacturing processes, but rather as a completely different and new production paradigm, suitable for particular situations, most of the time in highly technical contexts, that completely changes the structure of the value of the final product. Furthermore, this new paradigm has led to a democratization of manufacturing processes, especially with the accessibility of FDM or SLA printers that can now be purchased at an affordable price.